---
title: "wnv-s_weekly_reports"
format: html
editor: visual
---

## Weekly Data Report

Code Below:\
- clears environment\
- unloads packages\
- loads necessary packages\
- creates setting for plots

```{r}
source("scripts/config.R")

```

```{bash}
git commit -a -m "weekly commit before data removal"
git push

```

```{r}
source("scripts/dir_clean.R")

```

data_input: - reads in all datasheets types

```{r}
source("scripts/datasheet_read_clean.R")
```

data_input: platemap and quantstudio

```{r}
source("scripts/pcr_platemap_read_clean.R")
```

Code Below:\

```{r}
source("scripts/pcr_plot.R")
pcr_plot
```

Code Below:

-   data_input:
    -   active_traps.gsheet
    -   trap_malfunction.gsheet
-   data_output:
    -   fn_func_trap: data_mid/functional_traps.csv
-   description:
    -   pull and create list of functional traps (ones that are active that didn't malfunction)

```{r}
source("scripts/get_func_trap.R")
```

Code Below:

-   data_input:
    -   datasheets
    -   pcr_sheet
    -   platemap
    -   fn_func_trap: data_mid/functional_traps.csv \*to be added
-   data_output:
    -   fn_database_output
    -   unmatched traps
-   description:
    -   checks to ensure traps match existing list
    -   pulls database
    -   merges datasheet pcr and platemap data
    -   makes archive copy of database
    -   merges new data with database
    -   pushes changes from new data to database to googledrive

```{r}
source("scripts/data_merge_and_push.R")
```

Code Below: -data_input

```{r}
source("scripts/weekly_data_input.R")
```

Code Below:\
- data input:\
- data_input file and trap coordinates (if not in data_input)

```{r}
source('scripts/abundance_v2.R')
```

```{r}
source('scripts/pools.R')
```

Code Below:

Data Input:\
-output from abundance.R\
-data_input file:\
\
Data Output:\
-yYYYY_wWW_data_update\
\
Description:

\- calculates pooled Infection Rate and Vector Index\
-calculates all spp for each zone (TBD 24-07-16)

this script will drop weeks that only have a gravid trap. because gravid traps aren't used in abundance calculations

```{r}
source("scripts/pIR_VI.R")
```

```{r}
suppressMessages(
  source("scripts/historical_weekly.R")
)

p_hx_current
```

```{r}
source("scripts/tables.R")
```

Before generating tables and report make sure all the stuff is correct\

```{r}
#source("scripts/QC_report.R")
```

```{r}
suppressMessages(
  source("scripts/generate_report.R")
)
```
