---
title: "wnv-s_weekly_reports"
format: html
editor: visual
---

## Weekly Data Report

Code Below:\
- clears environment\
- unloads packages\
- loads necessary packages\
- creates setting for plots

```{r}
source("scripts/config.R")

```

Update trap locations?
-will look to see if the trap_col names exist, remove them then merge with trap_coord and overwrite all_data_fn

```{r}
#update_trap in config.R
if(update_trap == "YES") {
  source("scripts/trap_update.R")
}
```

```{r}
if(clean_data == "YES") {
  source("scripts/data_clean.R")
}
```



data_input: vdci
code below:
formats weekly report data to match existing database
```{r}
source("scripts/vdci_cdc_read_clean.R")
```

data_input: platemap and quantstudio
```{r}
source("scripts/QS_platemap_read_clean.R")
```

Code Below:\
 - merges weekly report with existing database
 -pulls data from gdrive and makes and archived copy in database_archive
 

```{r}
source("scripts/data_merge_and_push.R")
```

creates list to remove any traps that weren't found in the database in the current season or the previous. used in abundance.


Code Below:\
-data_input:\
  - active_traps.gsheet\
  - trap_malfunction.gsheet

-data_output:\
   - fn_func_trap: data_mid/functional_traps.csv
```{r}
source("scripts/get_func_trap.R")
```

Code Below:\
- data input:\
\-- data_input file and trap coordinates (if not in data_input)

```{r}
source('scripts/abundance_v2.R')
```


```{r}
source('scripts/pools.R')
```

Code Below:\
- calculates pooled Infection Rate and Vector Index

Data Input:\
-output from abundance.R\
-data_input file:\
\
Data Output:\
-yYYYY_wWW_data_update\
\
Notes: this script will drop weeks that only have a gravid trap. because gravid traps aren't used in abundance calculations

```{r}
source("scripts/pIR_VI.R")
```

```{r}
source("scripts/historical_weekly.R")
```

```{r}
source("scripts/tables.R")
```

```{r}
suppressMessages(
  source("scripts/generate_report.R")
)

```


```{r}
#source("scripts/data_viz.R")
```

```{r}
#source("scripts/map_data.R")
```
