---
title: "wnv-s_weekly_reports"
format: html
editor: visual
---

## Weekly Data Report

Code Below:\
- clears environment\
- unloads packages\
- loads necessary packages\
- creates setting for plots

```{r}
source("scripts/config.R")

```

\
Update trap locations?\
-will look to see if the trap_col names exist, remove them then merge with trap_coord and overwrite all_data_fn

```{r}
#update_trap in config.R
if(update_trap == "YES") {
  source("scripts/trap_update.R")
}
```

```{r}
if(clean_data == "YES") {
  source("scripts/data_clean.R")
}
```

Code Below:\
- checks if only one file is present in data_input/new_data folder\
- checks if it is a csv\
- if both true reads in data if not prints and error

```{r}
source("scripts/check_data.R")
```

Code Below:\
- data input:\
\-- data_input file and trap coordinates (if not in data_input)

```{r}
source('scripts/abundance.R')
```

Code Below:\
- calculates pooled Infection Rate and Vector Index

Data Input:\
-output from abundance.R\
-data_input file:\
\
Data Output:\
-yYYYY_wWW_data_update\
\
Notes: this script will drop weeks that only have a gravid trap. because gravid traps aren't used in abundance calculations

```{r}
source("scripts/pIR_VI.R")

```

```{r}
source("scripts/data_viz.R")

```
