---
title: "wnv-s_weekly_reports"
format: html
editor: visual
---

## Weekly Data Report

Code Below:\
- clears environment\
- unloads packages\
- loads necessary packages\
- creates setting for plots

```{r}
source("scripts/config.R")

```

```{bash}
# git add --all
 #git commit -m "weekly commit before data removal"
 #git push
  #rm -f data_input/cdc/* -->
# rm -f data_input/datasheet/* -->
#  rm -f data_input/pcr/* -->
# rm -f data_input/platemap/* -->
# rm -f data_mid/* -->
# rm -f data_output/* -->

```


data_input:
- reads in all datasheets types


```{r}
source("scripts/datasheet_read_clean.R")
```

data_input: platemap and quantstudio

```{r}
source("scripts/pcr_platemap_read_clean.R")
```

Code Below:\
- merges the cq_data (platemap and pcr results) with the datasheets
- creates the test_code threshold
- reads in database from google drive
- creates a copy to archive on googledirve
- merges weekly update with the database to make database_update
- pushs database_update to googledrive
- writes the weekly update to the mid folder

```{r}
source("scripts/pcr_plot.R")
pcr_plot
```

```{r}
source("scripts/data_merge_and_push.R")
```

Code Below:
-data_input 
```{r}
source("scripts/weekly_data_input.R")
```

creates list to remove any traps that weren't found in the database in the current season or the previous. used in abundance.

Code Below:\
-data_input:\
- active_traps.gsheet\
- trap_malfunction.gsheet

-data_output:\
- fn_func_trap: data_mid/functional_traps.csv

```{r}
source("scripts/get_func_trap.R")
```

Code Below:\
- data input:\
\-- data_input file and trap coordinates (if not in data_input)

```{r}
source('scripts/abundance_v2.R')
```

```{r}
source('scripts/pools.R')
```

Code Below:\
- calculates pooled Infection Rate and Vector Index

Data Input:\
-output from abundance.R\
-data_input file:\
\
Data Output:\
-yYYYY_wWW_data_update\
\
Notes: this script will drop weeks that only have a gravid trap. because gravid traps aren't used in abundance calculations

```{r}
source("scripts/pIR_VI.R")
```

```{r}
source("scripts/historical_weekly.R")

```

```{r}
source("scripts/tables.R")
```

```{r}
suppressMessages(
  source("scripts/generate_report.R")
)

```

```{r}
#source("scripts/data_viz.R")
```

```{r}
#source("scripts/map_data.R")
```
