-------------- CALC ABUNDANCE —————————————————–

DESC:DEPENDENCIES:INPUT:OUTPUT:

```{r}
#group by zone
abund0 = calc_abund(culex_new, 
                  grp_var = c("zone", "year", "week", "spp"))

#group FC
abund_fc = calc_abund(culex_new, 
                  grp_var = c("zone2", "year", "week", "spp"))

#group all spp
abund_all = calc_abund(culex_new, 
                  grp_var = c("zone", "year", "week"))

#group all FC
abund_all_fc = calc_abund(culex_new, 
                  grp_var = c("zone2", "year", "week"))

abund = bind_rows(abund0, abund_all, 
                  abund_fc, abund_all_fc) %>%
  distinct_all() %>%
  wnv_s_clean(all_cols = names(.)) %>%
  arrange(year, week, zone, spp)

check_data(df = abund,
           trap = foco_trap, 
           dir = dir_mid,
           year_filter = year_filter, 
           week_filter = week_filter
           )


write.csv(abund, fn_abund_out, row.names = F)


write.csv(culex_new, file.path(dir_mid, "abund_trap.csv"))
write.csv(abund0$trap, file.path(dir_mid, "abund_trap.csv"))
write.csv(abund0$grp, file.path(dir_mid, "abund.csv"))

rm(abund0, abund_fc, abund_all, abund_all_fc)
```


-------------- CALC PIR —————————————————–

Code Below:

Data Input:-output from abundance.R-data_input file:Data Output:-yYYYY_wWW_data_updateDescription:

- calculates pooled Infection Rate and Vector Index-calculates all spp for each zone (TBD 24-07-16)

this script will drop weeks that only have a gravid trap. because gravid traps aren't used in abundance calculations

```{r}
#add complete for the different zones
pir0 = calc_pir(database_new,
               grp_var = c("zone", "year", "week", "spp"))

pir_fc = calc_pir(database_new , 
                   grp_var = c("zone2", "year","spp", "week"))

pir_all = calc_pir(database_new , 
                   grp_var = c("zone", "year", "week"))

pir_fc_all = calc_pir(database_new, 
                   grp_var = c("zone2", "year", "week"))

pir = bind_rows(pir0, pir_all,
          pir_fc, pir_fc_all) %>% 
  distinct_all() %>%
  wnv_s_clean(all_cols = names(pir0)) %>%
  arrange(year, week, zone, spp)

write.csv(pir, file.path(dir_mid, "pir.csv"))

rm(pir0, pir_all, pir_fc, pir_fc_all)
```

-------------- CALC VI —————————————————–

```{r}
vi = calc_vi(abund, pir,
             by = grp_vars) %>%
   wnv_s_clean(rm_col = c("trap_status"))



